```{r}
library(ggplot2)
```

Here, we get the data from the csv and clean it up.
```{r}
chargingStations.year <- read.csv("Resources/10964_ev_charging_infrastructure_4-4-24.csv", header=TRUE, sep =",")
chargingStations.state <- read.csv("Resources/alt_fuel_stations (Nov 22 2024).csv", header=TRUE, sep =",")
chargingStations.year
chargingStations.state
```

First, the data set for year, only includes up until 2023, but our second data set was updated until 11/22/2024.
So, we can add the total count to a 2024 column in our year. Since we only care about the station locations, and not
the total number of ports (a station has multiple ports), we can do this.
```{r}
row2024 <- data.frame(Year = 2024, EV.Charging.Ports = NA, Station.Locations = nrow(chargingStations.state))

chargingStations.year <- rbind(chargingStations.year, row2024)

chargingStations.year
```

Let's visualize the growth of station locations over time.
```{r}
ggplot(chargingStations.year, aes(x = 2011:2024, y = Station.Locations)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "red", size = 2) +
  labs(
    title = "Charging Stations Present in US by Year",
    x = "Year",
    y = "Number of Stations"
  ) +
  theme_minimal()
```
Now, let's look at charging stations by State in 2024. First we must create a dataframe with the counts of each state present in the state dataframe, and then we can visualize it.
```{r}
stateCounts <- as.data.frame(table(chargingStations.state$State))
colnames(stateCounts) <- c("State", "Count")

stateCounts

ggplot(stateCounts, aes(x = State, y = Count / 100)) +
  geom_bar(stat = "identity", fill = "skyblue") + # `stat = "identity"` is for bar height defined by `y`
  labs(
    y = "Charging Stations Present (In Hundreds)", 
    x = "State"
  ) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90))
```

Sort the counts so that we can see the rankings. It might show a connection with our registration counts.
```{r}
sortedCounts <- stateCounts[order(stateCounts$Count, decreasing = TRUE), ]
sortedCounts
```
Let's observe the 5 number summary.
```{r}
summary(stateCounts)
```
