---
title: "Electric Car in America"
output: pdf_document
---

This is intended to be where we work, I am testing to see if I am able to push this
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
power.prop.test(p1=0.093,
                p2=0.120,
                sig.level = 0.05,
                n = 2000,
                #power = 0.90,
                alternative = "one.sided" )
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
power.prop.test(p1=0.093,
                p2=0.120,
                sig.level = 0.05,
                n = 2000,
                #power = 0.90,
                alternative = "one.sided" )
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
